Response to Pachter's Review

### 2020-02-02 index.Rmd
r2

```{r, warning=FALSE, echo = FALSE}
plot4 <- ggplot(df, aes(x=amscit))+
  geom_histogram(data=filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor"))),fill = "red", alpha = 0.2, binwidth = 1000) + 
  geom_histogram(data=filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor"))),fill = "blue", alpha = 0.2, binwidth = 1000) +
  geom_histogram(data=filter(df,( (lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor"))),fill = "green", alpha = 0.2, binwidth = 1000) +
  geom_vline(xintercept = mean(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")))$amscit, na.rm = TRUE), linetype="dotted", color = "red", size=1.5) +
  geom_vline(xintercept = mean(filter(df,( (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")))$amscit, na.rm = TRUE), linetype="dotted", color = "blue", size=1.5) +
  geom_vline(xintercept = mean(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")))$amscit, na.rm = TRUE), linetype="dotted", color = "green", size=1.5) +
  ggtitle("Math Sci Net Citations Comparison Professors (A=red), (B=blue), (C=green)")
plot4
```
```{r, echo = FALSE, include = FALSE}
mean(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
mean(filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
mean(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
median(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
median(filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
median(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
```

@@

```{r, include = FALSE, echo = FALSE}
muA <- mean(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")))$amscit, na.rm = TRUE)
muB <- mean(filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")))$amscit, na.rm = TRUE)
muC <- mean(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")))$amscit, na.rm = TRUE)

@@

n_a <- length(na.omit(filter(df, (lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor"))$amscit))
n_b <- length(na.omit(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor"))$amscit))
n_c <- length(na.omit(filter(df, (lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor"))$amscit))

@@

```{r , warning=FALSE, echo = FALSE}
plot9 <- ggplot(df, aes(x=amscitperyear))+
  geom_histogram(data=filter(df, (lettergroup == "A Only"|lettergroup == "A and B")),fill = "red", alpha = 0.2, binwidth = 50) + 
  geom_histogram(data=filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")),fill = "blue", alpha = 0.2, binwidth = 50) +
  geom_histogram(data=filter(df, (lettergroup == "C Only"|lettergroup == "B and C")),fill = "green", alpha = 0.2, binwidth = 50) +
  geom_vline(xintercept = mean(filter(df, (lettergroup == "A Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE), linetype="dotted", color = "red", size=1.5) +
  geom_vline(xintercept = mean(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE), linetype="dotted", color = "blue", size=1.5) +
  geom_vline(xintercept = mean(filter(df, (lettergroup == "C Only"|lettergroup == "B and C"))$amscitperyear, na.rm = TRUE), linetype="dotted", color = "green", size=1.5) +
  ggtitle("MathSciNet citperyear Comparison (A=red), (B=blue), (C=green)")
plot9
```

```{r, echo = FALSE, include= FALSE}
mean(filter(df, (lettergroup == "A Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "C Only"|lettergroup == "B and C"))$amscitperyear, na.rm = TRUE)
median(filter(df, (lettergroup == "A Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE)
median(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B"))$amscitperyear, na.rm = TRUE)
median(filter(df, (lettergroup == "C Only"|lettergroup == "B and C"))$amscitperyear, na.rm = TRUE)
```

The mean number of citations per year for signers of letter A is 16 and the median is 11.
The mean number of citations per year for signers of letter B is 41 and the median is 26.
The mean number of citations per year for signers of letter C is 56 and the median is 42.

@@

```{r, echo = FALSE, include = FALSE}
mean(filter(df, (lettergroup == "A Only"|lettergroup == "A and B")&role=="professor")$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&role=="professor")$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "C Only"|lettergroup == "B and C")&role=="professor")$amscitperyear, na.rm = TRUE)
```

@@

3. For letter C - 55.5451

>>>>

```{r, warning=FALSE, echo = FALSE}
plot4 <- ggplot(df, aes(x=amscit))+
  geom_histogram(data=filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&(role=="professor"))),fill = "red", alpha = 0.2, binwidth = 1000) + 
  geom_histogram(data=filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")&institution=="domesticr1"&field=="math")),fill = "blue", alpha = 0.2, binwidth = 1000) +
  geom_histogram(data=filter(df,( (lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&field=="math"&(role=="professor"))),fill = "green", alpha = 0.2, binwidth = 1000) +
  geom_vline(xintercept = mean(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")&institution=="domesticr1"&field=="math"))$amscit, na.rm = TRUE), linetype="dotted", color = "red", size=1.5) +
  geom_vline(xintercept = mean(filter(df,( (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")&institution=="domesticr1"&field=="math"))$amscit, na.rm = TRUE), linetype="dotted", color = "blue", size=1.5) +
  geom_vline(xintercept = mean(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")&institution=="domesticr1"&field=="math"))$amscit, na.rm = TRUE), linetype="dotted", color = "green", size=1.5) +
  ggtitle("Math Sci Net Citations Comparison Professors (A=red), (B=blue), (C=green)")
plot4
```
```{r, echo = FALSE,include=FALSE}
mean(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
mean(filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&institution=="domesticr1"&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
mean(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&(role=="professor")&(field=="math")))$amscit, na.rm = TRUE)
median(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor")&institution=="domesticr1"&(field=="math")))$amscit, na.rm = TRUE)
median(filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor")&institution=="domesticr1"&(field=="math")))$amscit, na.rm = TRUE)
median(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor")&institution=="domesticr1"&(field=="math")))$amscit, na.rm = TRUE)
```

@@

```{r, include = FALSE, echo = FALSE}
muA <- mean(filter(df, ((lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&(field=="math")&(role=="professor")))$amscit, na.rm = TRUE)
muB <- mean(filter(df, ((lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&institution=="domesticr1"&(field=="math")&(role=="professor")))$amscit, na.rm = TRUE)
muC <- mean(filter(df, ((lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&(field=="math")&(role=="professor")))$amscit, na.rm = TRUE)

@@

n_a <- length(na.omit(filter(df, institution=="domesticr1"&field=="math"&(lettergroup == "A Only"|lettergroup == "A and B")&(role=="professor"))$amscit))
n_b <- length(na.omit(filter(df, institution=="domesticr1"&field=="math"&(lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&(role=="professor"))$amscit))
n_c <- length(na.omit(filter(df, institution=="domesticr1"&field=="math"&(lettergroup == "C Only"|lettergroup == "B and C")&(role=="professor"))$amscit))

@@

```{r , warning=FALSE, echo = FALSE}
plot9 <- ggplot(df, aes(x=amscitperyear))+
  geom_histogram(data=filter(df, (lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor"),fill = "red", alpha = 0.2, binwidth = 50) + 
  geom_histogram(data=filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor"),fill = "blue", alpha = 0.2, binwidth = 50) +
  geom_histogram(data=filter(df, (lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&field=="math"&role=="professor"),fill = "green", alpha = 0.2, binwidth = 50) +
  geom_vline(xintercept = mean(filter(df, (lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE), linetype="dotted", color = "red", size=1.5) +
  geom_vline(xintercept = mean(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE), linetype="dotted", color = "blue", size=1.5) +
  geom_vline(xintercept = mean(filter(df, (lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE), linetype="dotted", color = "green", size=1.5) +
  ggtitle("MathSciNet citperyear Comparison (A=red), (B=blue), (C=green)")
plot9
```

```{r, echo = FALSE,include=FALSE}
mean(filter(df, (lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
median(filter(df, (lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
median(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
median(filter(df, (lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
```

The mean number of citations per year for signers of letter A is 16 and the median is 11.
The mean number of citations per year for signers of letter B is 42 and the median is 27.
The mean number of citations per year for signers of letter C is 55 and the median is 42.

@@

```{r, echo = FALSE,include=FALSE}
mean(filter(df, (lettergroup == "A Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "B and C"|lettergroup == "B Only"|lettergroup == "A and B")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
mean(filter(df, (lettergroup == "C Only"|lettergroup == "B and C")&institution=="domesticr1"&field=="math"&role=="professor")$amscitperyear, na.rm = TRUE)
```

@@

3. For letter C - 55.3615

### 2020-02-02 index.tex
r2

The mean number of citations per year for signers of letter A is 16 and
the median is 11. The mean number of citations per year for signers of
letter B is 41 and the median is 26. The mean number of citations per
year for signers of letter C is 56 and the median is 42.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  For letter A - 15.98726
\item
  For letter B - 41.86467
\item
  For letter C - 55.5451
\end{enumerate}

>>>>

The mean number of citations per year for signers of letter A is 16 and
the median is 11. The mean number of citations per year for signers of
letter B is 42 and the median is 27. The mean number of citations per
year for signers of letter C is 55 and the median is 42.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  For letter A - 15.98726
\item
  For letter B - 41.86467
\item
  For letter C - 55.3615
\end{enumerate}
